Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-05-29 manuscript.Rmd
More edits to Present Study section

Using cross-recurrence quantification analysis [CRQA; @zbilut1998detecting]
and windowed cross-recurrence quantification analysis
[WCRQA; @webber2005recurrence], we analyzed the co-evolution of social
cohesion online and real-world events. Specifically, using heterogeneous
data from March 30, 2012, to June 15, 2012, we compared the social cohesion
of Syrian tweets with the counts
of all, positive, and negative real-world events.

We hypothesized that the count of all events and the count of negative
events would show high levels of determinism, as this time period was
marked by daily violence which often leads to increased salience. We also
hypothesized that the count of positive events would not show patterns of
determinism, as these events were likely overshadowed by the salient
negative daily occurrences. 
After testing these hypotheses, we then conducted exploratory analyses 
to further examine the patterns identified with CRQA. Using WCRQA,
we sought to identify shifts in the
dynamics of the systems that could then be linked to real-world shifts in
conflict frequency.
Through these analyses, our primary goal in the current work was to uncover
(1) how different intensities during times of turmoil may enhance or deter
social cohesion in social media communication and (2) how social mobilization
may be evident in the dynamic coupling of cohesion and real-world events.

@@

# run primary crq analysis
source('./scripts/primary-analyses/02_crqa.R')

@@

# read in signficiance from permutation tests (target filtered)
sig_all_targ <- t(read.csv("./results/primary/crqa/target-metric_signif_all.csv", header = FALSE)[-1,-1])
sig_pos_targ <- t(read.csv("./results/primary/crqa/target-metric_signif_pos.csv", header = FALSE)[-1,-1])
sig_neg_targ <- t(read.csv("./results/primary/crqa/target-metric_signif_neg.csv", header = FALSE)[-1,-1])

@@

# read in signficiance from permutation tests (source and target filtered)
sig_all_source_targ <- t(read.csv("./results/primary/crqa/source_target-metric_signif_all.csv", header = FALSE)[-1,-1])
sig_pos_source_targ <- t(read.csv("./results/primary/crqa/source_target-metric_signif_pos.csv", header = FALSE)[-1,-1])
sig_neg_source_targ <- t(read.csv("./results/primary/crqa/source_target-metric_signif_neg.csv", header = FALSE)[-1,-1])

@@

## Cross-Recurrence Quantification Analysis
CRQA was performed using the crqa package [@R-crqa] for R [@R-base]. We 
conducted a permutation test to check for statistical difference from chance 
for all analyses and metrics.

>>>>

Using cross-recurrence quantification analysis [CRQA; @zbilut1998detecting]
and windowed cross-recurrence quantification analysis
[WCRQA; @webber2005recurrence], we analyzed the co-evolution of social
cohesion online and real-world events. Specifically, using heterogeneous
data from March 30, 2012, to June 15, 2012, we compared the social cohesion
of Syrian tweets with the counts
of all, positive, and negative real-world events derived from gold-standard
international event data [i.e., the Integrated Crisis Early Warning
System; @DVN/28075_2015].

We hypothesized that the count of all events and the count of negative
events would show high levels of determinism, as this time period was
marked by daily violence which often leads to increased salience. We also
hypothesized that the count of positive events would not show patterns of
determinism, as these events were likely overshadowed by the salient
negative daily occurrences. 
After testing these hypotheses, we then conducted exploratory analyses 
to further examine the patterns identified with CRQA. Using WCRQA,
we sought to identify shifts in the
dynamics of the systems that could then be linked to real-world shifts in
conflict frequency.
Through these analyses, our two primary goals in the current work were to uncover
(1) how different intensities during times of turmoil may enhance or deter
social cohesion in social media communication and (2) how social mobilization
may be evident in the dynamic coupling of cohesion and real-world events.

@@

# run primary crqa analysis
source('./scripts/primary-analyses/02_crqa.R')

@@

# read in significance from permutation tests (target filtered)
sig_all_targ <- t(read.csv("./results/primary/crqa/target-metric_signif_all.csv", 
                           header = FALSE)[-1,-1])
sig_pos_targ <- t(read.csv("./results/primary/crqa/target-metric_signif_pos.csv", 
                           header = FALSE)[-1,-1])
sig_neg_targ <- t(read.csv("./results/primary/crqa/target-metric_signif_neg.csv", 
                           header = FALSE)[-1,-1])

@@

# read in significance from permutation tests (source and target filtered)
sig_all_source_targ <- t(read.csv("./results/primary/crqa/source_target-metric_signif_all.csv", 
                                  header = FALSE)[-1,-1])
sig_pos_source_targ <- t(read.csv("./results/primary/crqa/source_target-metric_signif_pos.csv", 
                                  header = FALSE)[-1,-1])
sig_neg_source_targ <- t(read.csv("./results/primary/crqa/source_target-metric_signif_neg.csv", 
                                  header = FALSE)[-1,-1])

@@

## Cross-Recurrence Quantification Analysis
CRQA was performed using the `crqa` package [@R-crqa] for R [@R-base]. We 
conducted a permutation test to check for statistical difference from chance 
for all analyses and metrics.
